%-------------------------
% Resume in Latex
% Author : Son Nguyen
% Website: https://github.com/nosyn/my-resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Son Nguyen}} & Email : \href{mailto:nyenson1997@gmail.com}{nyenson1997@gmail.com}\\
  \href{https://nosyn.dev/}{https://nosyn.dev} & Mobile : +84 (797) - 050797 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University - Corpus Christi}{Corpus Christi, TX}
      {Bachelor of Science in Computer Science;  GPA: 3.92}{Aug. 2016 -- May. 2020}
 \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Code Engine Studio}{Da Nang, Vietnam}
      {Software Engineer - Dev Lead}{Sep 2023 - Present}
      \resumeItemListStart
        \resumeItem{Mai}
          {An AI platform, originated from the need of Code Engine Studio employees to efficiently search through company documents like policies and product information in a user-friendly manner. The platform enables users to access various AI providers like OpenAI, Google's Gemini, and Claude, and seamlessly integrates with popular chat platforms such as Mattermost, Slack, and Teams.}
        \resumeItem{Virtual Testing}
          {A comprehensive visual testing and review tool designed to scan all potential UI states across browsers, identifying visual and functional bugs efficiently. It facilitates assigning reviewers and resolving discussions to streamline team approval processes.}
      \resumeItemListEnd
    \resumeSubheading
      {Plus One Robotics}{San Antonio, TX}
      {Software Engineer}{Dec 2020 - June 2023}
      \resumeItemListStart
        \resumeItem{Yonder}
          {Yonder is a micro software suite that offers a "Human-In-The-Loop" remote supervisory solution for robotic applications. It features crew chiefs who can swiftly address production exceptions by remotely executing robotic tasks. The software's intelligent queue management allows one crew chief to handle multiple systems efficiently, with a multi-device, multi-user design for seamless use across platforms. Yonder provides a data dashboard highlighting critical KPIs and prioritizes user-centric security with fully encrypted cloud and on-premise network options. Yonder Analytic, an Elastic application, operates seamlessly on cloud and on-premises platforms, automatically scaling in response to varying workloads. It can manage over a hundred robots with distinct metrics, offering customized widgets to display robot performance over time. Yonder Analytic is designed to be highly available, fault-tolerant, and resilient, ensuring uninterrupted operation even when handling millions of requests from robots daily.}
        \resumeItem{PickOne Assistant }
          {PickOne Assistant is a configuration tool that allows for the rapid setup of pilot robot cells utilizing PickOne, an AI-driven vision software that provides accurate hand-eye coordination for logistics robots. The purpose of PickOne Assistant is to facilitate 80\% of new deployments and streamline the process of integrating with internal software, minimizing the associated challenges.}
      \resumeItemListEnd

    \resumeSubheading
      {Center for Academic Student Achievement  (CASA)}{Corpus Christi, TX}
      {Math tutor }{Aug 2018 - May 2020}
      \resumeItemListStart
        \resumeItem{Responsibilities}
          {As a math tutor, I provide academic support to college students in calculus, linear algebra, discrete math, and geometry. I work closely with students to help them improve their understanding of mathematical concepts, complete assignments, and prepare for exams. I create a positive and supportive learning environment, adapting to students' individual needs and learning styles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeSubItem{Gotcha}
      {A microservice application that uses Kafka to distribute data from backend systems to the web services.}
    \resumeSubItem{Snippetbox}
      {Snippetbox - GitHub gists alike -  is a simple way to share snippets and pastes of code with others. It allows users to create and share single files, parts of files, or full applications.}
    \resumeSubItem{Hulix}
      {Web based streaming movies application based on The MovieDB APIs.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {TypeScript, JavaScript, Golang, SQL, Python, Bash, HTML5, CSS3}
    \resumeSubItem{Technologies}
      {Google Cloud Platform, Amazon Web Services, OpenAI, LlamaIndex, Kubernetes, K3s, Terraform Docker, CI/CD, NodeJS, Kafka, WebSocket, ROS (Robot Operation System), Redis, Elastic, GraphQL}
    \resumeSubItem{Skills}
      {Agile, Teamwork, System Design, Microservices design, RESTful APIs design, Unit testing}
    \resumeSubItem{Frameworks/ Libraries}
      {ReactJS, NextJS, Apollo GraphQL, ReactQuery, Material UI, TailwindCSS, PixiJS, Jest, RxJS}
    \resumeSubItem{Databases}
      {PostgresQL, MongoDB}    
    \resumeSubItem{OS}
      {Linux, Windows, MacOS}
    \resumeSubItem{Tools}
      {VSCodes, Neovim, Git, GitHub, GitLab, Figma}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
