%-------------------------
% Resume in Latex
% Author : Son Nguyen
% Website: https://github.com/nosyn/my-resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Son Nguyen}} & Email : \href{mailto:nyenson1997@gmail.com}{nyenson1997@gmail.com}\\
  \href{https://nosyn.dev/}{https://nosyn.dev} & Mobile : +1-323-794-1359 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University - Corpus Christi}{Corpus Christi, TX}
      {Bachelor of Science in Computer Science;  GPA: 3.92}{Aug. 2016 -- May. 2020}
 \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Plus One Robotics}{San Antonio, TX}
      {Software Engineer}{Dec 2020 - Present}
      \resumeItemListStart
        \resumeItem{Yonder}
          {Yonder is a "Human-In-The-Loop" remote supervisor micro software suite for robotic applications that provides crew chiefs trained to step in and execute robotic work from afar to solve production exceptions within seconds. With smart queue management, one crew chief can handle many systems, and the multi-device, multi-user design allows seamless use for all. Yonder also provides a data dashboard that reveals business-relevant KPIs, and user-centric security standards with a fully encrypted cloud and on-premise network available to meet security needs.}
        \resumeItem{Yonder Analytic}
          {Yonder Analytic is a cloud and on-premises Elastic application that can automatically scale up or down based on changing workloads and resource requirements. As demand increases, more robots and metrics are added to the system to handle the additional load. It also analyzes and displays custom widgets that show the efficiency and performance of robots over time. Yonder Analytic is designed to be highly available, fault-tolerant, and resilient, ensuring that it can continue to operate with millions of requests from robots per day.}
        \resumeItem{AdminOne}
          {AdminOne is an internal web application that provides an internal dashboard for admin users to manage robots from the cloud. Admin can see real-time robot's state, logs, and software versions, etc. It also implements an RBAC system that allows admin users to manage the permissions of organizations and robots.}          
        \resumeItem{PickOne Assistant }
          {PickOne Assistant is a configuration tool for quick deployment of pilot robot cells using PickOne. PickOne is an AI-powered vision software that enables precise hand-eye coordination for logistics robots. PickOne Assistant is meant to handle 80\% of new deployments and ease the pain of integrating with internal software.}
      \resumeItemListEnd

    \resumeSubheading
      {Center for Academic Student Achievement  (CASA)}{Corpus Christi, TX}
      {Math tutor }{Aug 2018 - May 2020}
      \resumeItemListStart
        \resumeItem{Responsibilities}
          {As a math tutor, I provide academic support to college students in calculus, linear algebra, discrete math, and geometry. I work closely with students to help them improve their understanding of mathematical concepts, complete assignments, and prepare for exams. I create a positive and supportive learning environment, adapting to students' individual needs and learning styles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeSubItem{Gotcha}
      {A microservice application that uses Kafka to distribute data from backend systems to the web services.}
    \resumeSubItem{Snippetbox}
      {Snippetbox - GitHub gists alike -  is a simple way to share snippets and pastes of code with others. It allows users to create and share single files, parts of files, or full applications.}
    \resumeSubItem{Hulix - https://github.com/nosyn/hulix}
      {\newline
      Web based streaming movies application based on MovieDB APIs.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {TypeScript, JavaScript, Golang, SQL, Bash, HTML5, CSS3}
    \resumeSubItem{Technologies}
      {Google Cloud Platform, Kubernetes, Docker, Docker-compose, CI/CD, NodeJS, Kafka, WebSocket, ROS (Robot Operation System), Redis, Elastic}
    \resumeSubItem{Skills}
      {Agile, Teamwork, System Design, Microservices design}
    \resumeSubItem{Frameworks/ Libraries}
      {ReactJS, NextJS, Apollo GraphQL, Material UI, TailwindCSS, PixiJS}
    \resumeSubItem{Databases}
      {PostgresQL, MongoDB}    
    \resumeSubItem{Technologies}
      {Google Cloud Platform, Kubernetes, Docker, GraphQL, Docker-compose, CI/CD, NodeJS, Kafka, WebSocket, ROS (Robot Operation System), Redis, WebSocket, Elastic}
    \resumeSubItem{Tools}
      {VSCodes, Neovim, Git, GitHub, GitLab, Figma}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
